Effectiveness of private sector malaria control at a large sugar

### 2017-12-28 inst/rmd/paper.Rmd
update

```{r, results = 'asis'}
clean_up_model <- function(x){
  x = broom::tidy(x)
  for(j in 2:(ncol(x) -1)){
    x[,j] <- x[,j] * 100
  }
  x$term <- gsub('seasonhigh', 'High transmission season', x$term)
  x$term <- gsub('months_since', 'Months since IRS: ', x$term)
  x$term <- gsub('department', 'Department: ', x$term)
  x$term <- gsub('precipitation', 'Precipitation (mm) ', x$term)
  x$term <- gsub('maragra_fabricaTRUE', 'Living at factory', x$term)
  x$term <- gsub('sexM', 'Male', x$term)
  x$term <- gsub('permanent_or_temporaryTemporary', 'Temp contract', x$term)
  x$term <- gsub('rainyTRUE', 'Rainy day', x$term)
  names(x) <- Hmisc::capitalize(names(x))
  names(x) <- gsub('.', ' ', names(x), fixed = TRUE)
  x <- x %>% 
    mutate(Estimate = paste0(round(Estimate, 3), ' (P = ',
                             ifelse(`P value` <= 0.001,
                                    '< 0.001',
                                    round(`P value`, 4)), ')')) %>%
    dplyr::select(Term, Estimate)
  return(x)
}
# Combine them all
out_list <- list()
for (i in 1:length(models)){
  this_model <- letters[i]
  the_model <- models[[this_model]]
  the_model <- clean_up_model(the_model)
  names(the_model)[2] <- paste0('Model ', i)
  out_list[[i]] <- the_model
}
df <- out_list[[length(models)]]
for(i in (length(models) - 1):1){
  message(i)
    df <- left_join(df, out_list[[i]])
}
df <- df[,unique(c('Term', sort(names(df))))]
print(xtable::xtable(x, caption = ))

>>>>

```{r, results = 'asis'}
clean_up_model <- function(x){
  x = broom::tidy(x)
  for(j in 2:(ncol(x) -1)){
    x[,j] <- x[,j] * 100
  }
  x$term <- gsub('seasonhigh', 'Malaria season', x$term)
  x$term <- gsub('months_since', 'Months since IRS: ', x$term)
  x$term <- gsub('department', 'Department: ', x$term)
  x$term <- gsub('precipitation', 'Precipitation (mm) ', x$term)
  x$term <- gsub('maragra_fabricaTRUE', 'Living at factory', x$term)
  x$term <- gsub('sexM', 'Male', x$term)
  x$term <- gsub('permanent_or_temporaryTemporary', 'Temp contract', x$term)
  x$term <- gsub('rainyTRUE', 'Rainy day', x$term)
  names(x) <- Hmisc::capitalize(names(x))
  names(x) <- gsub('.', ' ', names(x), fixed = TRUE)
  x <- x %>% 
    mutate(Estimate = paste0(round(Estimate, 3), ' (P = ',
                             ifelse(`P value` <= 0.001,
                                    '< 0.001',
                                    round(`P value`, 4)), ')')) %>%
    dplyr::select(Term, Estimate)
  return(x)
}
# Combine them all
out_list <- list()
for (i in 1:length(models)){
  this_model <- letters[i]
  the_model <- models[[this_model]]
  the_model <- clean_up_model(the_model)
  names(the_model)[2] <- paste0('Model ', i)
  out_list[[i]] <- the_model
}
df <- out_list[[length(models)]]
for(i in (length(models) - 1):1){
  message(i)
    df <- left_join(df, out_list[[i]])
}
df <- df[,unique(c('Term', sort(names(df))))]
print(xtable::xtable(df, caption = 'Regression outputs'), size="\\fontsize{5pt}{6pt}\\selectfont")
